The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-24 article.tex
Sgroup example image.

%% TODO(JWM): Sgroup Examples

CTfile Sgroups capture and organise high level information about sets of atoms
and bonds \cite{Gushurst91}. There are four types of Sgroup: Display Shortcuts, Polymers,
Mixtures, and Data. The most familiar Sgroups from an end user perspective are structure 
repeat units (e.g. bracketing) and abbreviations (figure: ??). CDK \textbf{2.0} adds 
supports for representation, reading, writing, and depiction.

@@

\includegraphics[width=\textwidth]{sdg2.png}

@@

>>>>

CTfile Sgroups capture and organise high level information about sets of atoms
and bonds \cite{Gushurst91}. There are four types of Sgroup: Display Shortcuts, Polymers,
Mixtures, and Data. The most familiar Sgroups from an end user perspective are structure 
repeat units (e.g. bracketing) and abbreviations (Figure: 8\label{fig:sgroups}). CDK \textbf{2.0} adds 
supports for representation, reading, writing, and depiction.

@@

%\includegraphics[width=\textwidth]{sdg2.png}

@@

\subsection*{Figure 8 - Examples of Sgroups now captured by the CDK and encoded in molfiles and CXSMILES. a) Ethyl esterification fully expanded reaction. b) Using Sgroup abbreviations allows display short cuts and more compact depiction. c) An example of a structure repeat unit in \textit{DNA 5'-phosphate} (\textbf{CHEBI:4294})}
\label{fig:sgroups}

\includegraphics[width=\textwidth]{img/sgroups.pdf}
